### 2016-05-31 filters.tex
intro updates

\heading{Privacy of hash-based filters.} \tsnote{This is wide open.  Privacy of~$S$?  Privacy of~$M$?  (The latter may or may not imply the former, depending on how we define things.)  }

>>>>

\heading{Privacy of hash-based filters.} \tsnote{This is wide open.  Privacy of~$S$?  Privacy of~$M$?  (The latter may or may not imply the former, depending on how we define things.)  Under what assumptions on~$S$ --~min-entropy, computational unguessability, other? Do we want to allow for explicit side information/precomputation? We want something that captures realistic scenarios.}

### 2016-05-31 intro.tex
hacking syntax
intro updates

\heading{Our contributions. }
Given these shortcomings and the prevalent use of Bloom filters in practice, we revisit the matter of formalizing them as primitives with explicit security goals, these goals being abstracted from the attack surface they expose in practice.   We begin by giving a new syntax for an approximate-set-membership primitive (ASM) that clearly captures Bloom filters... \tsnote{finish}

We provided various security notions for ASMs... FP with private, public representation coins; set privacy with private, public representation coins; FP/set privacy in the multi-representation setting (outsider attack, think CDNs); FP/set privacy in the multi-representation setting with corruptions (insider attack, think P2P networks) \tsnote{Those are just the ones that come to mind now.  Could also consider authenicity of representations, think CDN or P2P settings.}

Later, we give syntax for ASM primitives that also admit operations upon the set representation.  This captures so-called counting Bloom filters that are used, for example, in fairness-enforcing algorithms for routing of TCP streams.  It also captures...

@@

\heading{Related work. }
Mitzenmacher and Vadhan.

>>>>

\heading{Our contributions. }
Given these shortcomings and the prevalent use of Bloom filters in practice, we revisit the matter of formalizing them as primitives with explicit security goals, these goals being abstracted from the attack surface they expose in practice.   We begin by giving a new syntax for hash-based filters, which more clearly captures Bloom filters...

We generalize this syntax to hash-based filters that are mutable, in the sense that they allow for updating of the representation.  This allows us to capture counting Bloom filters, spectral Bloom filters, stable Bloom filters, count-min sketches, and other compact set respresentation data structures...

We provide various security notions for these primitives... FP with private, public representation coins; set privacy with private, public representation coins; FP/set privacy in the multi-representation setting (outsider attack, think CDNs); FP/set privacy in the multi-representation setting with corruptions (insider attack, think P2P networks) \tsnote{Those are just the ones that come to mind now.  Could also consider authenicity of representations, think CDN or P2P settings.}

@@

\heading{Related work. }
Niedermayer et al., breaking privacy of secret-hash-function Bloom filters.
Mitzenmacher and Vadhan.\tsnote{Might only be tangential.}
